Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-13 rates-neurips-21/rates.tex
minor

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
In this paper, we assume $\R$ is a finite set.
For example, standard binary classification has $\Y = \R = \{-1,+1\}$.
In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
In a ranking problem, $\R$ is the set of all permutations of $\Y$.

@@

We give two main results to deepen this understanding.
The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
\begin{theorem}
  Let $L$ be a polyhedral surrogate and $\psi$ a link function such that $(L,\psi)$ is consistent for a target loss $\ell$.
  Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}
The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.

\begin{theorem}
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}

>>>>

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
In this paper, we assume $\R$ is a finite set.
For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas
% In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
in a ranking problem, $\R$ is the set of all permutations of $\Y$.

@@

We give two main results to deepen this understanding.
The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.

\begin{theorem}
  Let $L$ be a polyhedral surrogate and $\psi$ a link function such that $(L,\psi)$ is consistent for a target loss $\ell$.
  Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}
\begin{theorem}
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
